---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

HappyDB is a corpus of 100,000 crowd-sourced happy moments via Amazon's Mechanical Turk. You can read more about it on https://arxiv.org/abs/1801.07746.

Here, we explore this data set and try to answer the question, "What makes people happy?"

### Loading in libraries to be used

```{r load libraries, warning=FALSE, message=FALSE}
library(tm)
library(tidytext)
library(tidyverse)
library(DT)
library(scales)
library(wordcloud2)
library(gridExtra)
library(ngram)
library(shiny) 
```

### Load the data to be cleaned and processed

```{r read data, warning=FALSE, message=FALSE}
urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/cleaned_hm.csv'
hm_data <- read_csv(urlfile)
```

### Preliminary cleaning of text

-We clean the text by converting all the letters to the lower case, and removing punctuation, numbers, empty words and extra white space.

```{r text processing in tm}
corpus <- VCorpus(VectorSource(hm_data$cleaned_hm))%>%
  tm_map(content_transformer(tolower))%>%
  tm_map(removePunctuation)%>%
  tm_map(removeNumbers)%>%
  tm_map(removeWords, character(0))%>%
  tm_map(stripWhitespace)
```

### Stemming words and converting tm object to tidy object

```{r stemming}
stemmed <- tm_map(corpus, stemDocument) %>%
  tidy() %>%
  select(text)
```

### Creating tidy format of the dictionary to be used for completing stems

-For the ability to look up the words corresponding to the stems.

```{r tidy dictionary}
dict <- tidy(corpus) %>%
  select(text) %>%
  unnest_tokens(dictionary, text)
```

### To remove stopwords that don't hold any significant information for our data set

-We remove stopwords provided by the "tidytext" package and also add custom stopwords in context of our data.

```{r stopwords}
data("stop_words")

word <- c("happy","ago","yesterday","lot","today","months","month",
                 "happier","happiest","last","week","past")

stop_words <- stop_words %>%
  bind_rows(mutate(tibble(word), lexicon = "updated"))
```

### Combining stems and dictionary into the same tibble

Here we combine the stems and the dictionary into the same "tidy" object.

```{r tidy stems with dictionary}
completed <- stemmed %>%
  mutate(id = row_number()) %>%
  unnest_tokens(stems, text) %>%
  bind_cols(dict) %>%
  anti_join(stop_words, by = c("dictionary" = "word"))
```

### Stem completion

Lastly, we complete the stems by picking the corresponding word with the highest frequency.

```{r stem completion, warning=FALSE, message=FALSE}
completed <- completed %>%
  group_by(stems) %>%
  count(dictionary) %>%
  mutate(word = dictionary[which.max(n)]) %>%
  ungroup() %>%
  select(stems, word) %>%
  distinct() %>%
  right_join(completed) %>%
  select(-stems)
```

### Pasting stem completed individual words into their respective happy moments


```{r reverse unnest}
completed <- completed %>%
  group_by(id) %>%
  summarise(text = str_c(word, collapse = " ")) %>%
  ungroup()
```

### Keeping a track of the happy moments with their own ID

```{r cleaned hm_data, warning=FALSE, message=FALSE}
hm_data <- hm_data %>%
  mutate(id = row_number()) %>%
  inner_join(completed)

datatable(hm_data)
```

### Exporting the processed text data into a CSV file to be used

```{r export data}
write_csv(hm_data, "processed_moments.csv")
```


### Load the processed text data along with demographic information on contributors

-use the processed data for our analysis and combine it with the demographic information available.

```{r load data, warning=FALSE, message=FALSE}
hm_data <- read_csv("processed_moments.csv")

urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/demographic.csv'
demo_data <- read_csv(urlfile)
```

### Combine both the data sets and keep the required columns for analysis

To select a subset of the data that satisfies specific row conditions

```{r combining data, warning=FALSE, message=FALSE}
hm_data <- hm_data %>%
  inner_join(demo_data, by = "wid") %>%
  select(wid,
         original_hm,
         gender, 
         marital, 
         parenthood,
         reflection_period,
         age, 
         country, 
         ground_truth_category, 
         text) %>%
  mutate(count = sapply(hm_data$text, wordcount)) %>%
  filter(gender %in% c("m", "f")) %>%
  filter(marital %in% c("single", "married")) %>%
  filter(parenthood %in% c("n", "y")) %>%
  filter(reflection_period %in% c("24h", "3m")) %>%
  mutate(reflection_period = fct_recode(reflection_period, 
                                        months_3 = "3m", hours_24 = "24h"))
```

```{r}
datatable(hm_data)
```
### Create a bag of words using the text data

```{r bag of words, warning=FALSE, message=FALSE}
bag_of_words <-  hm_data %>%
  unnest_tokens(word, text)

word_count <- bag_of_words %>%
  count(word, sort = TRUE)
```

### Create bigrams using the text data

```{r bigram, warning=FALSE, message=FALSE}
hm_bigrams <- hm_data %>%
  filter(count != 1) %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

bigram_counts <- hm_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  count(word1, word2, sort = TRUE)
```



